### 2024-04-11 project1/nsSurvey.tex
new

$$\rho(g(X)), $$

where $X \in \Omega$. 
$g(X)$ can't be directly evaluated, but it is the output of

$$ g(X) = \mathbb{E}\left[ Y|X=x \right]\vert_{x=X} $$

Some common risk measures are in the nested expectation form, in which 
$$\rho(g(X)) = \mathbb{E}\left[ h(g(X)) \right]$$

where $h(\cdot)$ is a known function. 
Forms of $h$ include the following:
\begin{itemize}
    \item 	Smooth functions, e.g., a quadratic tracking error with benchmark $b$: $h(t) = (t - b)^2$
    \item 	Lipschitz continuous functions, e.g., a mean excess loss over threshold $u$: $h(t) = \max\{t - u, 0\}$. Here, $h$ is a hockey-stick function.
    \item 	Indicator functions, e.g., probability of a large loss over a threshold $u$: $h(t) = \mathbb{I}_{\{t \geqslant u\}}$
\end{itemize}

Other risk measures of interest that are not in the nested expectation form are the value at risk (VaR) and the conditional value at risk (CVaR). 
The $\alpha$-VaR of $g(X)$ is defined as
$$
    \mbox{VaR}_\alpha(g(X)) = q_\alpha = \inf \left\{ q: \Pr(g(X)\leq q) \geq \alpha \right\}.
$$
The $\alpha$-CVaR of $g(X)$ is defined as
$$
    \mbox{VaR}_\alpha(g(X)) =\frac{1}{1-\alpha} \int_{\alpha}^{1} q_v dv. 
$$

@@

The standard nested simulation procedure estimates $g(X_i)$ with a standard Monte Carlo estimator

$$\hat{g}_N(X_i) = \frac{1}{N} \sum_{j=1}^N Y_{ij}; ~~~ Y_{ij} \sim F_{Y|X_i} $$

Let $(\hat{g}_N(\mathbf{X}))_{[1]}, \dots, (\hat{g}_N(\mathbf{X}))_{[M]}$ be the order statistics of $\hat{g}_N(X_1), \dots \hat{g}_N(X_M)$. 
The standard nested simulation estimators for different forms of $\rho$ are as follows:

\begin{enumerate}
    \item   Nested expectation form:
            $$\hat{\rho}_{M, N} = \frac{1}{M} \sum_{i=1}^M h(\hat{g}_N(X_i)) = \frac{1}{M} \sum_{i=1}^M h(\bar{Y}_{N, i}); ~~~ X_i \sim F_X$$
    \item   Value at risk (VaR):
            $$\hat{\rho}_{M, N} = (\hat{g}_N(\mathbf{X}))_{\lceil \alpha M \rceil}$$
    \item   Conditional value at risk (CVaR):
            $$\hat{\rho}_{M, N} = (\hat{g}_N(\mathbf{X}))_{\lceil \alpha M \rceil} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{g}_N(X_i) - (\hat{g}_N(\mathbf{X}))_{\lceil \alpha M \rceil}, 0 \}$$
\end{enumerate}

~\cite{gordy2010nested} analyze the optimal budget allocation of the standard nested simulation procedure with respect to the MSE of the estimator $\hat{\rho}_{M, N}$.

@@

\begin{equation*}
    \hat{\rho}^{\text{MLMC}}_\Gamma = \sum_{\ell=0}^{L} \left( \frac{1}{M_{\ell}} \sum_{i=1}^{M_{\ell}} h(\hat{g}_{N_{\ell}}(X_{i, \ell})) - \frac{1}{M_{\ell-1}} \sum_{i=1}^{M_{\ell-1}} h(\hat{g}_{N_{\ell-1}}(X_{i, \ell-1})) \right), ~~~ X_{i, \ell} \sim F_X,
\end{equation*}

where $\hat{g}_N(\cdot) = 0$, $L$ is the number of levels, $M_{\ell}$ is the number of outer scenarios at level $\ell$, and $N_{\ell}$ is the number of inner replications at level $\ell$.
Applying the analysis of~\cite{giles2015multilevel} in a nested simulation context,~\cite{giles2019multilevel} show that the MLMC method can achieve a similar level of accuracy as the standard nested simulation procedure with a lower total computational budget.
The simulation budget $\Gamma$ is the sum of the computational budget at each level, that is, $\Gamma = \sum_{\ell=0}^{L} M_{\ell} \cdot N_{\ell}$.

@@

In supervised learning, $g(\cdot)$ can be approximated by $\hat{g}^{\text{SL}}_{M, N}(\cdot)$, which is based on a chosen function family $\mathcal{G}$ and observations from the standard nested simulation procedure.
Consider the observation pairs $(X_i, \hat{g}_N(X_i))$ for $i \in \{1, \dots, M\}$ as training data, we can use supervised learning to approximate $g(\cdot)$ by $\hat{g}^{\text{SL}}_{M, N}(\cdot)$ and to pool the inner replications from all outer scenarios.
Using the $M$ \textit{training} samples, a nested Monte Carlo estimator of $\rho$ is given by

\begin{enumerate}
    \item   Nested expectation form:
            $$\hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \frac{1}{M} \sum_{i=1}^M h(\hat{g}^{\text{SL}}_{M, N}(X_i)); ~~~ X_i \sim F_X$$
    \item   VaR:
            $$\hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = (\hat{g}^{\text{SL}}_{M, N}(\mathbf{X}))_{\lceil \alpha M \rceil}$$
    \item   CVaR:
            $$\hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = (\hat{g}^{\text{SL}}_{M, N}(\mathbf{X}))_{\lceil \alpha M \rceil} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{g}^{\text{SL}}_{M, N}(X_i) - (\hat{g}^{\text{SL}}_{M, N}(\mathbf{X}))_{\lceil \alpha M \rceil}, 0 \}$$
\end{enumerate}
where $(\hat{g}_{M, N}(\mathbf{X}))_{\lceil \alpha M \rceil}$ is the $\lceil \alpha M \rceil$-th order statistic of $\hat{g}^{\text{SL}}_{M, N}(X_1), \dots, \hat{g}_{M, N}(X_M)$.
Similarly, with $M'$ \textit{test} samples of $X$, namely $\tilde{\mathbf{X}} = \tilde{X}_1, \dots, \tilde{X}_{M'}$, an estimator is given by

\begin{enumerate}
    \item   Nested expectation form:
            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = \frac{1}{M'} \sum_{i=1}^{M'} h(\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_i)); ~~~ \tilde{X}_i \sim F_X.$$
    \item   VaR:
            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M' \rceil}.$$
    \item   CVaR:
            \begin{align*}
                \hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} & = (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M' \rceil}  \\
                & + \frac{1}{(1-\alpha) M'} \sum_{i=1}^{M'} \max \{\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_i) - (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M' \rceil}, 0 \}, 
            \end{align*}
\end{enumerate}
where $(\hat{g}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M' \rceil}$ is the $\lceil \alpha M' \rceil$-th order statistic of $\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_1), \dots, \hat{g}_{M, N}(\tilde{X}_{M'})$. 
Note that $\hat{g}^{\text{SL}}_{M, N}(\cdot)$ is derived from the training samples $(X_1, \hat{g}_N(X_1)), \dots, (X_M, \hat{g}_N(X_M))$.

We are interested in minimizing the MSE of the supervised learning-based nested simulation estimator with supervised learning $\hat{\rho}^{\text{SL}, \text{Train}}_{M, N}$ and $\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'}$ subject to the total simulation budget $\Gamma$.

@@

Existing literature on nested simulation procedures has proposed different methods to approximate the true function $g(\cdot)$ with supervised learning algorithms. 
Methods that include theoretical convergence results are regression~\citep{broadie2015risk}, kernel smoothing~\citep{hong2017kernel}, and kernel ridge regression~\citep{wang2022smooth}.
Their estimators of $g(\cdot)$ are given by $\hat{g}^{\text{REG}}_{M, N}(\cdot)$, $\hat{g}^{\text{KS}}_{M, N}(\cdot)$, and $\hat{g}^{\text{KRR}}_{M, N}(\cdot)$, respectively.

\begin{itemize}
    \item   Regression:
            $$\hat{g}^{\text{REG}}_{M, N}(X) = \Phi(X) \hat{\beta},$$
            where $\Phi$ is a chosen basis, and $\hat{\beta}$ is estimated from the training samples.
    \item   Kernel smoothing:
            $$\hat{g}^{\text{KS}}_{M, N}(X) = \frac{\sum_{i=1}^M \bar{Y}_{N, i} K_w(X - X_i)}{\sum_{i=1}^M K_w(X - X_i)}, $$
            where $K_w$ is the kernel function with bandwidth $w$.
    \item   Kernel ridge regression:
            $$\hat{g}^{\text{KRR}}_{M, N}(X) = \argmin_{g \in \mathcal{N}_{\Psi}(\Omega)} \left( \frac{1}{M} \sum_{i=1}^M (\hat{g}_N(X_i) - g(X_i))^2 + \lambda \|g\|_{\mathcal{N}_{\Psi}(\Omega)}^2\right),$$
            where $\mathcal{N}_{\Psi}(\Omega)$ is the reproducing kernel Hilbert space (RKHS) with kernel $\Psi$ defined domain $\Omega$, and $\lambda$ is the regularization parameter as in ridge regression. 
            More specifically, $\Phi$ is a Mat\'ern kernel with smoothness parameter $\nu$ and length scale parameter $\ell$.
\end{itemize}

@@

Instead of using a supervised learning model as proxy,~\cite{zhang2022sample} uses the likelihood ratio weights to pool the inner replications from all outer scenarios.
Here, we restrict our attention to problems in the nested expectation form whose outer scenarios characterize the stochasticity of the inner simulation model. 
Specifically,
$$ Y = Y(H, X), $$
where $H$ is a random variable whose distribution is specified by the outer scenarios $X$. 
We denote the conditional distribution of $H|X$ by $f_{H|X}$. 
For a specific scenario $X_i$, we write $f_{H|X}(\cdot |X_i)$. 
To reconcile with previously established notations, we note that inner simulation outputs $Y_{ij}$ can be written as
$$ Y_{ij} = Y(H_{ij}, X_i), $$
where $H_{ij} \sim f_{H|X}(\cdot |X_i)$.
Suppose that one can generate random variable H from some sampling
distribution $f_H$. Then, the likelihood ratio estimator of $\rho$ is given by
$$\hat{\rho}^{\text{LR}}_{M,N} = \frac{1}{M} \sum_{i=1}^M h(\hat{g}^{\text{LR}}_N(X_i)), $$ where the inner replications are pooled by the likelihood ratio weights with
$$\hat{g}^{\text{LR}}_N(X_i) = \frac{1}{N} \sum_{j=1}^N Y(H_j, X_i) \frac{f_{H|X}(H_{j}|X_i)}{f_H(H_{ij})}, \;\;\; H_j \sim f_H, \;\;\; i=1, \dots, M.$$

With a total simulation budget $\Gamma$, we are interested in the order of convergence of estimators for all nested simulation procedures, which is measured by their MSE about the risk measure $\rho$.

@@

where $\Gamma$ is the total simulation budget for all nested simulation procedures considered in this study.
A special case is the MLMC method, where the total simulation budget $\Gamma$ is the sum of the computational budget at all levels.

@@

In~\cite{wang2022smooth}, the authors of the KRR-based nested simulation procedures claim to have bridged the gap between the cubic and square root convergence rates of nested simulation procedures. However, they analyze convergence in probabilistic order, and it is only applicable in terms of the absolute error. 
Instead of showing the convergence of the KRR-based estimator in terms of MSE as in~\cite{gordy2010nested}, we show the connections between the convergence in MSE and the convergence in probabilistic order for absolute error.
Our findings in Section~\ref{sec1:connection-mse-absolute-error} show that the analysis of ~\cite{wang2022smooth} indeed bridges the gap, but only in terms of the absolute error.

@@

\begin{definition}
    Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
    We write $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-k} \right)$, that is, $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $k$ if 
    $$
        \exists C \limsup_{M} \frac{\mathbb{E} \left[\left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-k}} \leq C
    $$
\end{definition}

\begin{definition}
    Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
    We write $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-k})$, that is $\hat{\rho}_{\Gamma}$ converges in probabilistic order $k$ to $\rho$ if for large enough $\Gamma$,
    $$
        \forall \epsilon > 0 \exists C \mathbb{P} \left( \left| \hat{\rho}_{\Gamma} - \rho \right| \geq C \Gamma^{-k} \right) \leq \epsilon 
    $$
\end{definition}

We start by showing the convergence in probabilistic order from the convergence in MSE.
Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-k} \right)$.
Then, from the definition of convergence in MSE, there exists a constant $C$ such that 
$$
    \limsup_{M} \frac{\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-k}} \leq C.
$$
Hence, there exists some $\Gamma$ such that for all $\gamma \geq \Gamma$,
$$
\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \right] \leq C\gamma^{-k}.
$$
The convergence in probabilistic order can be shown by separating the expectation into two parts: tail and non-tail.
$$
\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| \leq d\gamma^s\}} \right] + \mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\}} \right] \leq C\gamma^{-k}.
$$
The first term is always positive, and the second term can be bounded from below by the indicator function.
\begin{align*}
\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\}} \right] 
& \geq \mathbb{E} \left[ d^2 \gamma^{2s} \cdot \mathbb{I}\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\} \right] \\
& = d^2 \gamma^{2s} \cdot \mathbb{E} \left[ \mathbb{I}\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \} \right] \\
& = d^2 \gamma^{2s} \cdot \mathbb{P} \left(|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \right)
\end{align*}

>>>>

$$\rho(L) = \rho(L(X))$$

where $X \in \mathcal{X} \subset \mathbb{R}^d$, and $L = L(X)$ is a random variable whose distribution is characterized by $X$.
$L(X)$ can't be directly evaluated, but it is the output of

$$ L(X) = \mathbb{E}\left[ Y|X=x \right]\vert_{x=X} $$

Some common risk measures are in the nested expectation form, in which 
$$\rho(L) = \mathbb{E}\left[ h(L) \right]$$

where $h: \mathbb{R} \rightarrow \mathbb{R}$ is a known function. 
Common forms of $h$ includes smooth functions, Lipschitz continuous functions, and indicator functions.
The nested expectation form is a general form that covers many risk measures of interest in financial engineering by varying the function $h$.

\begin{definition} \label{def1:smooth}
    A function $h: \mathbb{R} \rightarrow \mathbb{R}$ is smooth if it is continuously differentiable up to the $n$-th order for some $n \in \mathbb{N}$, 
    and its $n$-th and $(n-m)$-th derivatives are bounded for some $m \in \mathbb{N}$ and $m < n$.
\end{definition}

A quadratic tracking error with a benchmark $b$ falls into this category, in which $h(t) = (t - b)^2$.
In the context of nested simulation, different procedures require different versions of Definition~\ref{def1:smooth} to specify the smoothness of $h$ for their convergence analysis.
Table~\ref{tab1:smoothness} summarizes the smoothness assumption of $h$ for different nested simulation procedures in the literature.

\begin{table}[ht!]
    \centering
    \begin{tabular}{lcc}
    \toprule
    \textbf{Nested Simulation Procedures} & $n$ & $m$ \\
    \midrule
    Regression & $2$ & $0$ \\
    Kernel smoothing & $3$ & $1$ \\
    Kernel ridge regression & $2$ & $1$ \\
    Likelihood ratio & $2$ & $1$ \\
    \bottomrule
    \end{tabular}
    \caption{Smoothness assumption of $h$ for different nested simulation procedures}
    \label{tab1:smoothness}
\end{table}

\begin{definition} \label{def1:lipschitz}
    A function $h: \mathbb{R} \rightarrow \mathbb{R}$ is Lipschitz continuous with Lipschitz constant $K$ if for all $t_1, t_2 \in \mathbb{R}$, 
    $$|h(t_1) - h(t_2)| \leq K|t_1 - t_2|.$$
\end{definition}

A mean excess loss over a threshold $u$ is defined by setting $h(t) = \max\{t - u, 0\}$, which is a special case of a Lipschitz continuous function.

\begin{definition} \label{def1:indicator}
    A function $h: \mathbb{R} \rightarrow \mathbb{R}$ is an indicator function if 
    $$h(t) = \mathbb{I}_{\{t \geq u\}}$$
    for some $u \in \mathbb{R}$.
\end{definition}

The probability of a large loss over a threshold $u$ is obtained by setting $h(t) = \mathbb{I}_{\{t \geq u\}}$.

Other risk measures of interest that are not in the nested expectation form are the value at risk (VaR) and the conditional value at risk (CVaR). 
The $\alpha$-VaR of $L$ is defined as
$$
    \mbox{VaR}_\alpha(L) = q_\alpha = \inf \left\{ q: \Pr(L\leq q) \geq \alpha \right\}.
$$
The $\alpha$-CVaR of $L$ is defined as
$$
    \mbox{CVaR}_\alpha(L) =\frac{1}{1-\alpha} \int_{\alpha}^{1} q_v dv. 
$$

@@

The standard nested simulation procedure estimates $L_i = L(X_i)$ with a standard Monte Carlo estimator

$$\hat{L}_{N, i} = \frac{1}{N} \sum_{j=1}^N Y_{ij}; ~~~ Y_{ij} \sim F_{Y|X_i} $$

Let $\hat{L}_{(i)}, \dots, \hat{L}_{(M)}$ be the order statistics of $\hat{L}_{N, 1}, \dots \hat{L}_{N, M}$. 
The standard nested simulation estimators for different forms of $\rho$ are as follows:

\begin{enumerate}
    \item   Nested expectation form:
            $$\hat{\rho}_{M, N} = \frac{1}{M} \sum_{i=1}^M h(\hat{L}_{N, i}) = \frac{1}{M} \sum_{i=1}^M h(\bar{Y}_{N, i}); ~~~ X_i \sim F_X$$
    \item   Value at risk (VaR):
            $$\hat{\rho}_{M, N} = \hat{L}_{(\lceil \alpha M \rceil)}$$
    \item   Conditional value at risk (CVaR):
            $$\hat{\rho}_{M, N} = \hat{L}_{(\lceil \alpha M \rceil)} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{L}_{N, i} - \hat{L}_{(\lceil \alpha M \rceil)}, 0 \}$$
\end{enumerate}

~\cite{gordy2010nested} analyze the optimal budget allocation of the standard nested simulation procedure with respect to the MSE of the estimator $\hat{\rho}_{M, N}$ for hockey-stick $h$, indicator $h$, and VaR.

@@

\begin{equation*}
    \hat{\rho}^{\text{MLMC}}_\Gamma = \sum_{\upsilon=0}^{\Upsilon} \left( \frac{1}{M_{\upsilon}} \sum_{i=1}^{M_{\upsilon}} h(\hat{L}_{N_{\upsilon}}(X_{i, \upsilon})) - \frac{1}{M_{\upsilon-1}} \sum_{i=1}^{M_{\upsilon-1}} h(\hat{L}_{N_{\upsilon-1}}(X_{i, \upsilon-1})) \right), ~~~ X_{i, \upsilon} \sim F_X,
\end{equation*}

where $\hat{L}_{N_{-1}}(\cdot) = 0$, $\Upsilon$ is the number of levels, $M_{\upsilon}$ is the number of outer scenarios at level $\upsilon$, and $N_{\upsilon}$ is the number of inner replications at level $\upsilon$.
Applying the analysis of~\cite{giles2015multilevel} in a nested simulation context,~\cite{giles2019multilevel} show that the MLMC method can achieve a similar level of accuracy as the standard nested simulation procedure with a lower total computational budget.
The simulation budget $\Gamma$ is the sum of the computational budget at each level, that is, $\Gamma = \sum_{\upsilon=0}^{\Upsilon} M_{\upsilon} \cdot N_{\upsilon}$.

@@

Supervised learning-based nested simulation procedures treat the estimation of $L(\cdot)$ as a supervised learning problem. 
In supervised learning, $L(\cdot)$ can be approximated by $\hat{L}^{\text{SL}}_{M, N}(\cdot)$, which is based on a chosen function family and observations from the standard nested simulation procedure.
Consider the observation pairs $(X_i, \hat{L}_{N, i})$ for $i \in \{1, \dots, M\}$ as training data, we can use supervised learning to approximate $L_i$ by $\hat{L}_{M, N}^{\text{SL}}(X_i)$ and to pool the inner replications from all outer scenarios.
More specifically, $\hat{L}^{\text{SL}}_{M, N}(\cdot)$ denotes the supervised learning model trained on $(X_i, \hat{L}_{N, i})$ for $i \in \{1, \dots, M\}$, which is the simulation output of the standard nested simulation procedure with $M$ outer scenarios and $N$ inner replications. 
Using the $M$ \textit{training} samples, a nested Monte Carlo estimator of $\rho$ is given by

\begin{enumerate}
    \item   Nested expectation form:
            $$\hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \frac{1}{M} \sum_{i=1}^M h(\hat{L}^{\text{SL}}_{M, N}(X_i)); ~~~ X_i \sim F_X$$
    \item   VaR:
            $$\hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \hat{L}^{\text{SL}}_{(\lceil \alpha M \rceil)}$$
    \item   CVaR:
            $$\hat{\rho}^{\text{SL}, \text{Train}}_{M, N} = \hat{L}^{\text{SL}}_{(\lceil \alpha M \rceil)} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{L}^{\text{SL}}_{M, N}(X_i) - \hat{L}^{\text{SL}}_{(\lceil \alpha M \rceil)}, 0 \}$$
\end{enumerate}
where $\hat{L}_{(\lceil \alpha M \rceil)}$ is the $\lceil \alpha M \rceil$-th order statistic of $\hat{L}^{\text{SL}}_{M, N}(X_1), \dots, \hat{L}_{M, N}(X_M)$.

After a supervised learning model is trained, it can be used to make predictions for all $X \in \mathcal{X}$.
Instead of using the same training samples to estimate the risk measure, we can use predictions of a new set of $M'$ \textit{test} samples of $X$, namely $\tilde{\mathbf{X}} = \tilde{X}_1, \dots, \tilde{X}_{M'}$.
The resulting supervised learning-based estimator of $\rho^{\text{SL}, \text{Test}}$ is given by

\begin{enumerate}
    \item   Nested expectation form:
            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = \frac{1}{M'} \sum_{i=1}^{M'} h(\hat{L}^{\text{SL}}_{M, N}(\tilde{X}_i)); ~~~ \tilde{X}_i \sim F_X.$$
    \item   VaR:
            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = \hat{L}^{\text{SL}}_{(\lceil \alpha M' \rceil)}.$$
    \item   CVaR:
            \begin{equation*}
                \hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} 
                = \hat{L}^{\text{SL}}_{(\lceil \alpha M' \rceil)} 
                + \frac{1}{(1-\alpha) M'} \sum_{i=1}^{M'} \max \{\hat{L}^{\text{SL}}_{M, N}(\tilde{X}_i) - \hat{L}^{\text{SL}}_{(\lceil \alpha M' \rceil)}, 0 \}, 
            \end{equation*}
\end{enumerate}
where $\hat{L}^{\text{SL}}_{(\lceil \alpha M' \rceil)}$ is the $\lceil \alpha M' \rceil$-th order statistic of $\hat{L}^{\text{SL}}_{M, N}(\tilde{X}_1), \dots, \hat{L}^{\text{SL}}_{M, N}(\tilde{X}_{M'})$. 
Note that $\hat{L}^{\text{SL}}_{M, N}(\cdot)$ is the model preditions of a supervised learning model trained on the training samples $(X_1, \hat{L}_{N, 1}), \dots, (X_M, \hat{L}_{N, M})$.

We are interested in minimizing the MSE of the supervised learning-based nested simulation estimator with supervised learning $\hat{\rho}^{\text{SL}, \text{Train}}_{M, N}$ and $\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'}$ subject to the total simulation budget $\Gamma$, and we are interested in the order of convergence of the estimator for all nested simulation procedures when the total simulation budget $\Gamma$ approaches infinity.

@@

Existing literature on nested simulation procedures has proposed different methods to approximate the true function $L(\cdot)$ with supervised learning models. 
Methods that include theoretical convergence results are regression~\citep{broadie2015risk}, kernel smoothing~\citep{hong2017kernel}, and kernel ridge regression~\citep{wang2022smooth}.
Their estimators of $L(\cdot)$ are given by $\hat{L}^{\text{REG}}_{M, N}(\cdot)$, $\hat{L}^{\text{KS}}_{M, N}(\cdot)$, and $\hat{L}^{\text{KRR}}_{M, N}(\cdot)$, respectively.

\begin{itemize}
    \item   Regression:
            $$\hat{L}^{\text{REG}}_{M, N}(X) = \Phi(X) \hat{\beta},$$
            where $\Phi$ is a chosen basis, and $\hat{\beta}$ is estimated from the training samples.
    \item   Kernel smoothing:
            $$\hat{L}^{\text{KS}}_{M, N}(X) = \frac{\sum_{i=1}^M \bar{Y}_{N, i} K_w(X - X_i)}{\sum_{i=1}^M K_w(X - X_i)}, $$
            where $K_w$ is the kernel function with bandwidth $w$.
    \item   Kernel ridge regression:
            $$\hat{L}^{\text{KRR}}_{M, N}(X) = \argmin_{g \in \mathcal{N}_{\Psi}(\Omega)} \left( \frac{1}{M} \sum_{i=1}^M (\hat{L}_{N, i} - L_i)^2 + \lambda \|L\|_{\mathcal{N}_{\Psi}(\Omega)}^2\right),$$
            where $\mathcal{N}_{\Psi}(\Omega)$ is the reproducing kernel Hilbert space (RKHS) with kernel $\Psi$ defined domain $\Omega$, and $\lambda$ is the regularization parameter as in ridge regression. 
            More specifically, $\Phi$ is a Mat\'ern kernel with smoothness parameter $\nu$ and length scale parameter $\upsilon$.
\end{itemize}

These supervised learning models approximates the inner simulation model $L(\cdot)$ with a function $\hat{L}^{\text{SL}}_{M, N}(\cdot)$, and they are used to pool the inner replications from all outer scenarios to estimate the risk measure $\rho$.
In simulation literature, using models to approximate simulation is often referred to as the metamodeling approach, or it is referred to as a proxy model in the financial engineering literature.
Supervised learning models are broadly classified into regression and classification models depending on whether the traget variable $L$ is continuous or discrete.
In our context, the target variable $L$ is continuous, and the supervised learning models refer to regression models.
Regression models can be further categorized into parametric and non-parametric regression.
Among our interested supervised learning models, regression is a parametric regression model, while kernel smoothing and kernel ridge regression are non-parametric regression model.

@@

Instead of using a supervised learning model as a proxy,~\cite{zhang2022sample} uses the likelihood ratio weights to pool the inner replications from all outer scenarios.
Here, we restrict our attention to problems in the nested expectation form whose outer scenarios characterize the stochasticity of the inner simulation model. 
Specifically,
$$ Y = Y(H, X), $$
where $H$ is a random variable whose distribution is specified by the outer scenarios $X$. 
We denote the conditional distribution of $H|X$ by $f_{H|X}$. 
For a specific scenario $X_i$, we write $f_{H|X}(\cdot |X_i)$. 
To reconcile with previously established notations, we note that inner simulation outputs $Y_{ij}$ can be written as
$$ Y_{ij} = Y(H_{ij}, X_i), $$
where $H_{ij} \sim f_{H|X}(\cdot |X_i)$.
Suppose that one can generate random variable H from some sampling
distribution $f_H$. Then, the likelihood ratio estimator of $\rho$ is given by
$$\hat{\rho}^{\text{LR}}_{M,N} = \frac{1}{M} \sum_{i=1}^M h(\hat{L}^{\text{LR}}_{N, i}), $$ where the inner replications are pooled by the likelihood ratio weights with
$$\hat{L}^{\text{LR}}_{N, i} = \frac{1}{N} \sum_{j=1}^N Y(H_j, X_i) \frac{f_{H|X}(H_{j}|X_i)}{f_H(H_{ij})}, \;\;\; H_j \sim f_H, \;\;\; i=1, \dots, M.$$

\subsection{Problem Statement}

With a total simulation budget $\Gamma$, we are interested in the orders of convergence of estimators for all nested simulation procedures, which are measured by their MSE about the risk measure $\rho$.

@@

where $\Gamma$ is the total simulation budget for a nested simulation procedure.
A special case is the MLMC method, where the total simulation budget $\Gamma$ is the sum of the simulation budgets at all levels.

@@

In~\cite{wang2022smooth}, the authors of the KRR-based nested simulation procedures claim to have bridged the gap between the cubic and square root convergence rates of nested simulation procedures. However, they analyze convergence in probabilistic order, and it is only applicable in terms of the absolute error. 
Instead of showing the convergence of the KRR-based estimator in terms of MSE as in~\cite{gordy2010nested}, we show the connections between the convergence in MSE and the convergence in probabilistic order for absolute error.
Our findings in Section~\ref{sec1:connection-mse-absolute-error} show that the analysis of ~\cite{wang2022smooth} indeed bridges the gap, but only in terms of convergence in probabilistic order for the absolute error.

@@

\begin{definition}
    Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
    We write $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-\xi} \right)$, that is, $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $\xi$ if 
    $$
        \exists C \limsup_{M} \frac{\mathbb{E} \left[\left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-\xi}} \leq C
    $$
\end{definition}

\begin{definition}
    Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
    We write $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-\xi})$, that is $\hat{\rho}_{\Gamma}$ converges in probabilistic order $\xi$ to $\rho$ if for a sufficiently large $\Gamma$,
    $$
        \forall \epsilon > 0 \exists C \mathbb{P} \left( \left| \hat{\rho}_{\Gamma} - \rho \right| \geq C \Gamma^{-\xi} \right) \leq \epsilon 
    $$
\end{definition}

We start by showing the convergence in probabilistic order from the convergence in MSE.
Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-\xi} \right)$.
Then, from the definition of convergence in MSE, there exists a constant $C$ such that 
$$
    \limsup_{M} \frac{\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-\xi}} \leq C.
$$
Hence, there exists some $\Gamma$ such that for all $\gamma \geq \Gamma$,
$$
\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \right] \leq C\gamma^{-\xi}.
$$
The convergence in probabilistic order can be shown by separating the expectation into two parts: tail and non-tail.
$$
\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| \leq d\gamma^s\}} \right] + \mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\}} \right] \leq C\gamma^{-\xi}.
$$
The first term is always positive, and the second term can be bounded from below by the indicator function.
\begin{align*}
\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\}} \right] 
& \geq \mathbb{E} \left[ d^2 \gamma^{2s} \cdot \mathbb{I}\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\} \right] \\
& = d^2 \gamma^{2s} \cdot \mathbb{E} \left[ \mathbb{I}\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \} \right] \\
& = d^2 \gamma^{2s} \cdot \mathbb{P} \left(|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \right)
\end{align*}
